%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Introduction to Compiler Design} % Role
    {C- Compiler} % Title
    {Hsinchu, Taiwan} % Location
    {2018.9 - 2019.1} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented the C- compiler which understands the C- language and generates the corresponding JAVA Bytecode.}
        \item {Created the lexical analyzer and parser generator with the help of lex and yacc respectively.}
      \end{cvitems}
    }
    
  \cventry
    {JAVA Programming} % Role
    {IDE with multi-language supports} % Title
    {Hsinchu, Taiwan} % Location
    {2017.2 - 2017.6} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and implemented an Integrated Development Environment in java.}
        \item {Supported multiple programming languages such as C/C++, JAVA, and Python.}
      \end{cvitems}
    }
    
  \cventry
    {Electrical Engineering Projects} % Role
    {Predict the game results of NBA Using Deep Learning} % Title
    {Hsinchu, Taiwan} % Location
    {2017.2 - 2017.6} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Trained the deep neural network model and predicted the game results of NBA. }
        \item {Crawled the NBA game statistics from the ESPN websites and preserved the data in the SQL server.}
      \end{cvitems}
    }
    
  \cventry
    {Advanced Object-Oriented Programming} % Role
    {Fantasy Circuit} % Title
    {Hsinchu, Taiwan} % Location
    {2016.9 - 2017.1} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and implemented the circuit analyzer which provides an Graphic User Interface (GUI) to draw the specific circuit schema.}
        \item Analyzed the circuit schema by solving the node equations and plotted the result voltage waveform for any circuit node. 
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
